Emulating the CFHTLenS Weak Lensing data: Cosmological Constraints from moments and Minkowski functionals

### 2015-05-22 Paper_minkowski/Submission/reply/reply_referee.tex

\begin{document}

\title{Reply to referee's comments, DC11786/Petri}
\author{}
\date{}

\maketitle

\noindent
We thank the referee for the interesting and insightful comments, which we address in this document. The additions and modifications in the manuscript have been highlighted in blue.

@@

\begin{itemize}
\item \textit{Some cited papers do not match the description}: the desctiptions and references have been updated. The suggested references have been added.
\item \textit{Missing reference to Simon et. al.}: the reference has been added.
\item \textit{Explain the $\dot{\beta}$ notation and the meaning of $\dot{\beta}=0$}: the derivative is taken with respect to the comoving distance $\chi$; an initial condition for the derivative is required to make the Cauchy problem well defined. The appropriate explanation has been added to the text.
\item \textit{Explain why the random rotations of galaxies make the lensing signal $O(\kappa^2)$}: the galaxy shapes measured by CFHTLenS contain both contributions from the original galaxy shape and lensing contributions from LSS. The lensing contributions are spatially correlated and the spatial correlations are $O(\psi)$ where $\psi$ is the lensing potential ($\kappa=O(\psi)$ also). When we rotate each galaxy randomly, we destroy these spatial correlations, which will not be $O(\psi)$ anymore, but $O(\psi^2)$ or smaller (if not zero at all). Assigning galaxy shapes drawing from $\mathcal{N}(0,\sigma_\epsilon)$ would require knowledge of $\sigma_\epsilon$, which depends on redshift, galaxy luminosity, and on galaxy type. Since we do not have this information, randomly rotating galaxies is much simpler; it is also more accurate since it avoids making the assumption the intrinsic shape distribution is Gaussian to begin with.  

@@

\item \textit{Definition of $\Theta$ and $\delta_D$}: the definitions of the $\Theta$ and $\delta_D$ functions have been added in the appropriate section
\item \textit{Cubic and quartic moments notations}: we are aware that the definitions of $S_i,K_i$ we adopt are different than the ones provided in [38,39]. Within our statistical framework, these definitions mismatches do not matter as they are related to each other via a constant linear transformation that drops out in the likelihood calculations. The typo $K_4\leftrightarrow K_3$ has been corrected. 

@@

\item \textit{Confusion between $R=1000$ and the 50 independent $N$--body runs in \texttt{CFHTcov}}: the covariance matrices are always estimated from the $R=1000$ lensing field realizations. We believe that the $R$ realizations in the \texttt{CFHTcov} ensemble are more independen than the ones in the \texttt{CFHTemu1} ensemble due to the fact that \texttt{CFHTcov} is bases on 50 independent $N$--body runs. An appropriate explanation has been added to the text. 
\item \textit{Equation (15) (now equation (16)}: here, as throughout the paper, $R=1000$. We added the appropriate clarification
\item \textit{"For this reason, the normalization constant in equation (12) is also model--independent"}: the sentence has been deleted

### 2015-05-22 Paper_minkowski/paper.tex

%ZH: changed title a bit
\title{Emulating the CFHTLenS Weak Lensing data:  Cosmological Constraints from Moments and Minkowski Functionals}

@@

%ZH: I reworded the abstract
\begin{abstract}
Weak gravitational lensing is a powerful cosmological probe, with
non--Gaussian features potentially containing the majority of the
information. We examine constraints on the parameter triplet
$(\Omega_m,w,\sigma_8)$ from non-Gaussian features of the weak lensing
convergence field, including a set of moments (up to $4^{\rm th}$
order) and Minkowski Functionals, using publicly available data from
the 154\,deg$^2$ CFHTLenS survey. We utilize a suite of ray--tracing
N-body simulations spanning 91 points in $(\Omega_m,w,\sigma_8)$
parameter space, replicating the galaxy sky positions, redshifts and
shape noise in the CFHTLenS catalogs. We then build an emulator that
interpolates the simulated features as a function of
$(\Omega_m,w,\sigma_8)$, and use it to compute the likelihood function
and parameter constraints. We employ a principal component analysis to
reduce dimensionality and to help stabilize the constraints with
respect to the number of bins used to construct each statistic. Using
the full set of statistics, we find
$\Sigma_8\equiv\sigma_8(\Omega_m/0.27)^{0.55}=0.75\pm0.04$ (68\%
C.L.), in agreement with previous values. We find that constraints on
the $(\Omega_m,\sigma_8)$ doublet from the Minkowski Functionals
suffer a strong bias. However, high-order moments break the
$(\Omega_m,\sigma_8)$ degeneracy and provide a tight constraint on
these parameters with no apparent bias.  The main contribution comes
from quartic moments of gradients.
\end{abstract}

@@

In this work, we use the publicly available CFHTLenS data, consisting
of a catalog of $\approx$4.2 million galaxies, combined with a suite
of ray-tracing simulations in 91 different cosmological models to
derive constraints on the cosmological parameters $\Omega_m$,
$\sigma_8$ and the dark energy (DE) equation of state $w$.  The
statistics we consider in this work are the Minkowski Functionals
(MFs) and the low--order moments (LM) of the convergence field.
%ZH: I moved this here from the simulation section. Fits better here.
Cosmological parameter inferences from CFHTLenS have been obtained
using the 2PCF~\citep{CFHTKilbinger}, and a number of authors have
investigated the constraining power of CFHTLenS using statistics that
go beyond the usual quadratic ones. Fu et al.~\citep{CFHTFu} used
three--point correlations as an additional probe for cosmology, and
found modest ($10-20\%$) improvements over the 2PCF.  Liu et
al.~\citep{Companion} have found a more significant ($50-60\%$)
tightening of the $\Omega$ and $\sigma_8$ constraints, utilizing the
abundance of WL peaks.
%ZH: We should also cite the CFHT Stripe82 paper by the Chinese, using peak counts, here.
Finally, closest to the present paper, Shirasaki \&
Yoshida~\citep{CFHTMasato} investigated constraints from Minkowski
Functionals, including systematic errors.  Our study represents two
major improvements over previous work.  First, constraints from the
MFs in~ref.~\citep{CFHTMasato} were obtained through the Fisher matrix
formalism, assuming linear dependence on cosmological parameters. Our
study utilizes a suite of simulations sampling the cosmological
parameter space, mapping out the non-linear parameter-dependence of
each descriptor.  Second, we include the LMs as a set of new
descriptors; these yield to the tightest and least biased constraints.

This paper is organized as follows: we first give an overview of the
CFHTLenS catalogs, and summarize the adopted data reduction
techniques. Next, we give a description of our simulation pipeline,
including the ray--tracing algorithm, and the procedure used to sample
the parameter space. We call the statistical weak lensing observables
-- the Power Spectrum, Minkowski Functionals, and Moments --
"descriptors" throughout the paper. We discuss the calculation of the
descriptors, including dimensional reduction using a principal
component analysis, and the statistical inference framework we
used. We then describe our main results, i.e. the cosmological
parameter constraints. To conclude, we then discuss our findings and
comment on possible future extensions of this analysis.

@@

We next give a description of our method to sample the parameter space
with a suite of N--body simulations. We wish to investigate the
non--linear dependence of the descriptors (in this work, Minkowski
Functionals and moments of the $\kappa$ field) on the parameter
triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping the other
relevant parameters $(h,\Omega_b,n_s)$ fixed to the values (0.7,
0.046, 0.96). 
%ZH: cite WMAP9 paper here for the parameter choices.
We sampled the $D$--dimensional ($D=3$ in this case) parameter space
using an irregularly spaced grid. The grid was designed with a method
similar to that used to construct an emulator for the matter power
spectrum in the \texttt{Coyote} simulation suite \citep{coyote2}.
Given fixed available computing resources, the irregular grid design
is more efficient than a parameter grid with regular spacings: to
achieve the same average spacing between models in the latter approach
would require a prohibitively large number of simulations.

@@

Once we obtain the light ray trajectories, we infer the relevant weak
lensing quantities by taking angular derivatives of the ray
deflections $A(\chi_s;\pmb{\theta}) = \partial
\pmb{\beta}(\chi_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing
the usual spin decomposition to infer the convergence $\kappa$ and the
shear components $(\gamma^1,\gamma^2)$,
%
%AP: Inspector Gadget was never published.
%ZH: Yes.  That's a pity.  I added the reference to Jan's first paper instead.
%
\begin{equation}
A(\chi_s;\pmb{\theta}) = (1-\kappa(\chi_s;\pmb{\theta}))\pmb{I} - \gamma^1(\chi_s;\pmb{\theta})\sigma^3 - \gamma^2(\chi_s;\pmb{\theta})\sigma^1
\end{equation}  
%
where $\pmb{I}$ is the $2\times2$ identity and $\sigma^{1,3}$ are the
first and third Pauli matrices. The convergence $\kappa$ is related to
the magnification, while the two components of the complex shear
$\pmb{\gamma}=\gamma^1 + i\gamma^2$ are related to the apparent
ellipticity of the source. Given a source with intrinsic complex
ellipticity $\mathbf{e}_s=e^1_s + ie^2_s$, its observed ellipticity
will be modified to
%
\begin{equation}
\mathbf{e} = 
\begin{cases}
\frac{\mathbf{e}_s+\mathbf{g}}{1+\mathbf{g}^*\mathbf{e}_s} \,\,\,\,\,\,\,\, \vert \mathbf{g}\vert \leq 1 \\ \\
\frac{1+\mathbf{ge}_s^*}{\mathbf{e}_s^* + \mathbf{g}^*} \,\,\,\,\,\,\,\, \vert \mathbf{g}\vert > 1
\end{cases}
\end{equation}
%
where $\mathbf{g} \equiv \pmb{\gamma}/(1-\kappa)$ is the reduced shear.

@@

In addition to the MFs and LMs, we consider the angular power spectrum
$P_l\equiv P^2_l$ of $\kappa$, defined as
\begin{equation}
\label{powerspectrum}
\langle\tilde{\kappa}(\mathbf{l})\tilde{\kappa}(\mathbf{l}')\rangle=(2\pi)^2\delta_D(\mathbf{l}+\mathbf{l}')P_l,
\end{equation}  
%
where $\tilde{\kappa}(\mathbf{l})$ is the Fourier transform of the
$\kappa$ field and $\delta_D$ is the usual Dirac delta
function. Previous works have studied cosmological constraints from
the convergence power spectrum extensively.  Here our purpose is to
compare the constraints we obtain from the MFs and LMs to ones present
in the literature, which are based on the use of quadratic statistics
(see for example \citep{CFHTKilbinger}). The statistical descriptors
used in this work are summarized in Table \ref{desctable}.
%
\begin{table}
\begin{tabular}{c|c|c} \hline
Descriptor & Details & $N_b$ \\ \hline
$V_0,V_1,V_2$ (MF) & $\kappa_0\in[-0.04,0.12]$ & 50 \\
Power Spectrum (PS) & $l \in [300,5000]$ & 50 \\
Moments (LM) & -- & 9 \\
\end{tabular}
\caption{Summary of the descriptors we used, together with the specifications and the number of bins $N_b$ in each case.}
\label{desctable}
\end{table}
%

When measuring statistical descriptors on $\kappa$ maps, particular
attention must be paid to the effect of masked pixels. The MFs and LMs
remain well--defined in the presence of masks, since the estimators in
equations~(\ref{v1meas}) and (\ref{momentestimator}) are defined
locally, and can be computed in the non--masked regions (with the
exception of the few pixels that are close to the mask
boundaries). The situation is more complicated for power spectrum
measurements, which require the evaluations of Fourier transforms and
hence rely on the value of every pixel in the map. Although
sophisticated schemes to interpolate over the masked regions have been
studied (see for example \citep{VplasInterpolation}), for the sake of
simplicity, we here insert the value $\kappa=0$ in each masked pixel.
Given the typical angular size of the masked regions we consider, this
will have little effect on the power spectrum at the range of
multipoles in Table \ref{desctable}. 
%ZH: can you be more specific above and say what you mean by the angular scales?  Masks are much smaller than
%    the scales over which moments are defined?   Or much bigger?
Likewise, we believe that the way we deal with masked sky regions --
essentially ignoring them -- is robust for the MFs and LMs. Since we
apply the same masks to our simulations and the data, they are
unlikely to introduce biases in the resulting constraints.  Masks, of
course, can still affect the sensitivity and weaken constraints. The
impact of the masks and their treatment has been evaluated for the
MFs, obtained from CFHTLenS, by ref.~\citep{CFHTMasato}.
%ZH:  I think we need to state here something on what they found.

%AP: Stressed the fact that we apply the same mask to the simulations; added reference to Yoshida/Shirasaki 
%AP: I do not think the discussion on masked pixels is misleading: I just wanted to say that the estimators for MF and Moments are well defined also in the presence of masked pixels, while the PS estimator is not
%ZH:  OK, I rewrote above to say this.  I think what you mean to say here is that our results will not be biased,
%     since we apply the same masking to the data and the sims.   But there's still a separate question of loosing
%     sensitivity, which I noted above.

@@

In this section, we briefly outline of the statistical framework
adopted for computing cosmological parameter confidence levels.  We
make use of the MFs and LMs, as well as the power spectrum, as
discussed in the previous section. We refer to $M_i^r(\mathbf{p})$ as
the descriptor measured from a realization $r$ of one of our
simulations with a choice of cosmological parameters $\mathbf{p}$
(i.e. from one of the $R=1000$ maps in this cosmology), and to $D_i$
as the descriptor measured from the CFHTLenS data.
%ZH: Important: we never describe that we have R=1000 realization of
%    each model, by random rotations and shifts of the single N-body run.
%    This should be added above, where the simulations and the ray-tracing is discussed.
In this notation, $i$ is an index that refers to the particular bin on
which the descriptor is evaluated (for example $i$ can range from 0 to
9 for the LM statistic and from 0 to $N_b-1$ for a MF measured in
$N_b$ different $\kappa$ bins).
%on $N_b$ different excursion sets.
%ZH: Similarly: we should insert 2-3 sentence above, where we discuss the descriptors,
%    to state what binning we used (and indicate the actual kappa values of the bin boundaries).

@@

We studied the accuracy of the emulator, built with the
\texttt{CFHTemu1} simulations, by interpolating the convergence
descriptors to the fiducial parameter setting
$(\Omega_m,w,\sigma_8)=(0.26,-1.0,0.8)$ and comparing the result to
the one expected from the \texttt{CFHTcov}
simulations. Figure~\ref{emulatorAccuracy} shows that our power
spectrum emulator has accuracy better than 10\% for the lower
multipoles, and comparable to 1\% for the higher multipoles. The MF
emulator has accuracy $\lesssim$10\% for the first 30 bins (which
correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates due
to numerical noise for the remaining 20 bins. We eliminate the
residual impact of these inaccuracies using a dimensionality reduction
framework, which we explain in the next section. Nevertheless, we do
not expect these inaccuracies to affect our
conclusions. Figure~\ref{emulatorAccuracy} demonstrates that our
emulator is able to distinguish a non--fiducial model from the
fiducial one within numerical errors.  We thus found no need to
implement a more sophisticated interpolation
scheme~\footnote{Following ref.~\citep{coyote2}, we have experimented
  with interpolations using a Gaussian Process, but did not find a
  significant improvement in accuracy over the much simpler polynomial
  scheme; this is in agreement with earlier results.}.
%ZH: we should add citation of Lloyd Knox's paper http://adsabs.harvard.edu/abs/2011ApJ...728..137S
%    which said GP is not worth the hassle....

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{Figures/emulator_accuracy.eps}
\end{center}
%ZH:  It would be really nice to show ``kappa'' and ``ell'' instead (or in addition) to ``i'' on the x axis.
%     Maybe use the top of the figure to label kappa's and ell's?  Or at least state the kappa and ell ranges in words.
\caption{Accuracy of the emulator based on the \texttt{CFHTemu1}
  simulations. The figure shows the difference between the descriptor
  interpolated at the fiducial parameter setting, and the descriptor
  expected from the \texttt{CFHTcov} simulations. The descriptors are
  shown in units of the standard deviation in each bin $i$ (determined
  from the diagonal elements of the \texttt{CFHTcov} covariance
  matrix). We show the accuracy results for the power spectrum (red)
  and the three Minkowski Functionals $V_0$ (green), $V_1$ (blue) and
  $V_2$ (black). For reference, we also show, using dashed lines, the
  difference between the expected \texttt{CFHTcov} descriptors and the
  interpolated descriptor at the non--fiducial point $\mathbf{p}=(0.8,-1.0,0.5)$.}
%ZH: This last one is chosen to lie along our 1 (or 2?) sigma contour, right?
%    We should then state this, and make the point that this is the interpolation accuracy we care about,
%    and our accuracy is indeed better than this.
\label{emulatorAccuracy}
\end{figure}

@@

In order to compute the principal components of our descriptor space,
we use the \texttt{CFHTemu1} simulations, which sample the
cosmological parameters at the $N=91$ points listed in Table
\ref{designtable}, and allow us to compute the $N\times N_b$ model
matrix $M_{pi}=M_i(\mathbf{p})$. Note that this is a rectangular
(non-square) matrix. Following a standard procedure (see, e.g.,
ref.~\citep{astroMLText}), we derive the {\it whitened} model matrix
$\tilde{M}_{pi}$, defined by subtracting the mean (over the $R=1000$
realizations) of each matrix element,
%ZH: you wrote ``bin'' here, but I changed it to matrix element. All NxN_bin entries are whitened, presumably.
and normalizing it by its variance. Next we proceed with a singular
value decomposition (SVD) of $\mathbf{\tilde{M}}$,
\begin{equation}
\label{svd}
\mathbf{U}\mathbf{S} \mathbf{V}^T=\frac{\mathbf{\tilde{M}}}{\sqrt{N-1}},
\end{equation}   
%
where $S_{ij}=S_i\delta_{ij}$ is a diagonal matrix and $V^T_{ij}$ is
the $j$--th coordinate ($j=1...N_b$) of the $i$--th principal
component ($i=1...\mathrm{min}[N_b,N]$) of $\mathbf{\tilde{M}}$, with
the index $j$ ranging from $0$ to $N_b-1$. By construction,
$\mathbf{V}$ is $\mathbf{p}$--independent.

@@

This section describes our main results, and is organized as follows.
We begin by showing the cosmological constraints from the CFHTLenS
data for the triplet $(\Omega_m,\sigma_8,w)$, as well as for an
alternative parameterization, $(\Sigma_8,\alpha,w)$, with
$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$.  We then use
our simulations to perform a robustness analysis of the parameter
confidence intervals with respect to the number of PCA components used
in the projection.
%We first use our simulations to perform a robustness analysis
%of the parameter confidence intervals with respect to the number of
%PCA components used in the projection. We then show the cosmological
%constraints from the CFHTLenS data.
%ZH: I reversed the order of the above two.  
%    It is better to first show the constraints,  and only THEN we can discuss their robustness.
%    Also I moved the discussion of \Sigma_8 down below.
We finally study whether the constraints can be tightened by combining
different descriptors. A summary with the complete set of results,
along with the relevant Figures, is shown in Table \ref{summarytable}.

>>>>

%ZH: changed title a bit
\title{Emulating the CFHTLenS Weak Lensing data:  Cosmological Constraints from moments and Minkowski functionals}

@@

%ZH: I reworded the abstract
\begin{abstract}
Weak gravitational lensing is a powerful cosmological probe, with
non--Gaussian features potentially containing the majority of the
information. We examine constraints on the parameter triplet
$(\Omega_m,w,\sigma_8)$ from non-Gaussian features of the weak lensing
convergence field, including a set of moments (up to $4^{\rm th}$
order) and Minkowski functionals, using publicly available data from
the 154\,deg$^2$ CFHTLenS survey. We utilize a suite of ray--tracing
N-body simulations spanning 91 points in $(\Omega_m,w,\sigma_8)$
parameter space, replicating the galaxy sky positions, redshifts and
shape noise in the CFHTLenS catalogs. We then build an emulator that
interpolates the simulated descriptors as a function of
$(\Omega_m,w,\sigma_8)$, and use it to compute the likelihood function
and parameter constraints. We employ a principal component analysis to
reduce dimensionality and to help stabilize the constraints with
respect to the number of bins used to construct each statistic. Using
the full set of statistics, we find
$\Sigma_8\equiv\sigma_8(\Omega_m/0.27)^{0.55}=0.75\pm0.04$ (68\%
C.L.), in agreement with previous values. We find that constraints on
the $(\Omega_m,\sigma_8)$ doublet from the Minkowski functionals
suffer a strong bias. However, high-order moments break the
$(\Omega_m,\sigma_8)$ degeneracy and provide a tight constraint on
these parameters with no apparent bias.  The main contribution comes
from quartic moments of derivatives.
\end{abstract}

@@

In this work, we use the publicly available CFHTLenS data, consisting
of a catalog of $\approx$4.2 million galaxies, combined with a suite
of ray-tracing simulations in 91 different cosmological models to
derive constraints on the cosmological parameters $\Omega_m$,
$\sigma_8$ and the dark energy (DE) equation of state $w$.  The
statistics we consider in this work are the Minkowski functionals
(MFs) and the low--order moments (LM) of the convergence field.
%ZH: I moved this here from the simulation section. Fits better here.
Cosmological parameter inferences from CFHTLenS have been obtained
using the 2PCF~\citep{CFHTKilbinger}, and a number of authors have
investigated the constraining power of CFHTLenS using statistics that
go beyond the usual quadratic ones. Fu et al.~\citep{CFHTFu} used
three--point correlations as an additional probe for cosmology, and
found modest ($10-20\%$) improvements over the 2PCF.  Liu et
al.~\citep{Companion} have found a more significant ($50-60\%$)
tightening of the $\Omega$ and $\sigma_8$ constraints, utilizing the
abundance of WL peaks. Cosmological constraints using WL peaks in CFHTLenS Stripe82 data
have also been investigated by Liu et. al.~\citep{Stripe82}. 
%ZH: We should also cite the CFHT Stripe82 paper by the Chinese, using peak counts, here.
Finally, closest to the present paper, Shirasaki \&
Yoshida~\citep{CFHTMasato} investigated constraints from Minkowski
Functionals, including systematic errors.  Our study represents two
major improvements over previous work.  First, constraints from the
MFs in~ref.~\citep{CFHTMasato} were obtained through the Fisher matrix
formalism, assuming linear dependence on cosmological parameters. Our
study utilizes a suite of simulations sampling the cosmological
parameter space, mapping out the non-linear parameter-dependence of
each descriptor.  Second, we include the LMs as a set of new
descriptors; these yield the tightest and least biased constraints.

This paper is organized as follows: we first give an overview of the
CFHTLenS catalogs, and summarize the adopted data reduction
techniques. Next, we give a description of our simulation pipeline,
including the ray--tracing algorithm, and the procedure used to sample
the parameter space. We call the statistical weak lensing observables
-- the power spectrum, Minkowski functionals, and moments --
"descriptors" throughout the paper. We discuss the calculation of the
descriptors, including dimensional reduction using a principal
component analysis, and the statistical inference framework we
used. We then describe our main results, i.e. the cosmological
parameter constraints. To conclude, we then discuss our findings and
comment on possible future extensions of this analysis.

@@

We next give a description of our method to sample the parameter space
with a suite of N--body simulations. We wish to investigate the
non--linear dependence of the descriptors (in this work, Minkowski
Functionals and moments of the $\kappa$ field) on the parameter
triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping the other
relevant parameters $(h,\Omega_b,n_s)$ fixed to the values (0.7,
0.046, 0.96) (see \citep{WMAP9}).
%ZH: cite WMAP9 paper here for the parameter choices.
We sampled the $D$--dimensional ($D=3$ in this case) parameter space
using an irregularly spaced grid. The grid was designed with a method
similar to that used to construct an emulator for the matter power
spectrum in the \texttt{Coyote} simulation suite \citep{coyote2}.
Given fixed available computing resources, the irregular grid design
is more efficient than a parameter grid with regular spacings: to
achieve the same average spacing between models in the latter approach
would require a prohibitively large number of simulations.

@@

Once we obtain the light ray trajectories, we infer the relevant weak
lensing quantities by taking angular derivatives of the ray
deflections $A(\chi_s;\pmb{\theta}) = \partial
\pmb{\beta}(\chi_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing
the usual spin decomposition to infer the convergence $\kappa$ and the
shear components $(\gamma^1,\gamma^2)$,
%
%AP: Inspector Gadget was never published.
%ZH: Yes.  That's a pity.  I added the reference to Jan's first paper instead.
%
\begin{equation}
A(\chi_s;\pmb{\theta}) = (1-\kappa(\chi_s;\pmb{\theta}))\pmb{I} - \gamma^1(\chi_s;\pmb{\theta})\sigma^3 - \gamma^2(\chi_s;\pmb{\theta})\sigma^1
\end{equation}  
%
where $\pmb{I}$ is the $2\times2$ identity and $\sigma^{1,3}$ are the
first and third Pauli matrices.

Randomly rotating and periodically translating each of the N--body
data cubes along the three axes before ray--tracing, we are able to generate
different realizations of the weak lensing fields $\kappa,\gamma_{1,2}$. We use 
these different random realizations to estimate the covariance matrices of our
descriptors.

The convergence $\kappa$ is related to
the magnification, while the two components of the complex shear
$\pmb{\gamma}=\gamma^1 + i\gamma^2$ are related to the apparent
ellipticity of the source. Given a source with intrinsic complex
ellipticity $\mathbf{e}_s=e^1_s + ie^2_s$, its observed ellipticity
will be modified to
%
\begin{equation}
\mathbf{e} = 
\begin{cases}
\frac{\mathbf{e}_s+\mathbf{g}}{1+\mathbf{g}^*\mathbf{e}_s} \,\,\,\,\,\,\,\, \vert \mathbf{g}\vert \leq 1 \\ \\
\frac{1+\mathbf{ge}_s^*}{\mathbf{e}_s^* + \mathbf{g}^*} \,\,\,\,\,\,\,\, \vert \mathbf{g}\vert > 1
\end{cases}
\end{equation}
%
where $\mathbf{g} \equiv \pmb{\gamma}/(1-\kappa)$ is the reduced shear.

@@

In addition to the MFs and LMs, we consider the angular power spectrum
$P_l\equiv P^2_l$ of $\kappa$, defined as
\begin{equation}
\label{powerspectrum}
\langle\tilde{\kappa}(\mathbf{l})\tilde{\kappa}(\mathbf{l}')\rangle=(2\pi)^2\delta_D(\mathbf{l}+\mathbf{l}')P_l,
\end{equation}  
%
where $\tilde{\kappa}(\mathbf{l})$ is the Fourier transform of the
$\kappa$ field and $\delta_D$ is the usual Dirac delta
function. Previous works have studied cosmological constraints from
the convergence power spectrum extensively.  Here our purpose is to
compare the constraints we obtain from the MFs and LMs to ones present
in the literature, which are based on the use of quadratic statistics
(see for example \citep{CFHTKilbinger}). The statistical descriptors
used in this work are summarized in Table \ref{desctable}.
%
\begin{table}
\begin{tabular}{c|c|c} \hline
Descriptor & Details & $N_b$ (linear spacing) \\ \hline
$V_0,V_1,V_2$ (MF) & $\kappa_0\in[-0.04,0.12]$ & 50 \\
Power Spectrum (PS) & $l \in [300,5000]$ & 50 \\
Moments (LM) & -- & 9 \\
\end{tabular}
\caption{Summary of the descriptors we used, together with the specifications and the number of bins $N_b$ in each case.}
\label{desctable}
\end{table}
%

When measuring statistical descriptors on $\kappa$ maps, particular
attention must be paid to the effect of masked pixels. The MFs and LMs
remain well--defined in the presence of masks, since the estimators in
equations~(\ref{v1meas}) and (\ref{momentestimator}) are defined
locally, and can be computed in the non--masked regions (with the
exception of the few pixels that are close to the mask
boundaries). The situation is more complicated for power spectrum
measurements, which require the evaluations of Fourier transforms and
hence rely on the value of every pixel in the map. Although
sophisticated schemes to interpolate over the masked regions have been
studied (see for example \citep{VplasInterpolation}), for the sake of
simplicity, we here insert the value $\kappa=0$ in each masked pixel.
Given the uniform spatial distribution of the masked regions in the data, we expect that masks have a little effect on the power spectrum at the range of
multipoles in Table \ref{desctable}, except for an overall normalization which will be the same both in the data and the simulations.  
%ZH: can you be more specific above and say what you mean by the angular scales?  Masks are much smaller than
%    the scales over which moments are defined?   Or much bigger?
Likewise, we believe that the way we deal with masked sky regions --
essentially ignoring them -- is robust for the MFs and LMs. Since we
apply the same masks to our simulations and the data, they are
unlikely to introduce biases in the resulting constraints.  Masks, of
course, can still affect the sensitivity and weaken constraints. The
impact of the masks and their treatment has been evaluated for the
MFs, obtained from CFHTLenS, by ref.~\citep{CFHTMasato}, in which the authors find that the masked regions 
are not a dominant source of systematic effects in the CFHTLenS data. 
%ZH:  I think we need to state here something on what they found.

%AP: Stressed the fact that we apply the same mask to the simulations; added reference to Yoshida/Shirasaki 
%AP: I do not think the discussion on masked pixels is misleading: I just wanted to say that the estimators for MF and moments are well defined also in the presence of masked pixels, while the PS estimator is not
%ZH:  OK, I rewrote above to say this.  I think what you mean to say here is that our results will not be biased,
%     since we apply the same masking to the data and the sims.   But there's still a separate question of loosing
%     sensitivity, which I noted above.

@@

In this section, we briefly outline of the statistical framework
adopted for computing cosmological parameter confidence levels.  We
make use of the MFs and LMs, as well as the power spectrum, as
discussed in the previous section. We refer to $M_i^r(\mathbf{p})$ as
the descriptor measured from a realization $r$ of one of our
simulations with a choice of cosmological parameters $\mathbf{p}$
(i.e. from one of the $R=1000$ map realizations in this cosmology), and to $D_i$
as the descriptor measured from the CFHTLenS data.
In this notation, $i$ is an index that refers to the particular bin on
which the descriptor is evaluated (for example $i$ can range from 0 to
9 for the LM statistic and from 0 to $N_b-1$ for a MF measured in
$N_b$ different, linearly spaced $\kappa$ bins, as indicated in Table \ref{desctable}).
%on $N_b$ different excursion sets.
%ZH: Similarly: we should insert 2-3 sentence above, where we discuss the descriptors,
%    to state what binning we used (and indicate the actual kappa values of the bin boundaries).

@@

We studied the accuracy of the emulator, built with the
\texttt{CFHTemu1} simulations, by interpolating the convergence
descriptors to the fiducial parameter setting
$(\Omega_m,w,\sigma_8)=(0.26,-1.0,0.8)$ and comparing the result to
the one expected from the \texttt{CFHTcov}
simulations. Figure~\ref{emulatorAccuracy} shows that our power
spectrum emulator has accuracy better than 10\% for the lower
multipoles, and comparable to 1\% for the higher multipoles. The MF
emulator has accuracy $\lesssim$10\% for the first 30 bins (which
correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates due
to numerical noise for the remaining 20 bins. We eliminate the
residual impact of these inaccuracies using a dimensionality reduction
framework, which we explain in the next section. Nevertheless, we do
not expect these inaccuracies to affect our
conclusions. Figure~\ref{emulatorAccuracy} demonstrates that our
emulator is able to distinguish a non--fiducial model from the
fiducial one within numerical errors.  We thus found no need to
implement a more sophisticated interpolation
scheme~\footnote{Following ref.~\citep{coyote2}, we have experimented
  with interpolations using a Gaussian Process, but did not find a
  significant improvement in accuracy over the much simpler polynomial
  scheme; this is in agreement with earlier results (see for example \citep{KnoxGP})}.
%ZH: we should add citation of Lloyd Knox's paper http://adsabs.harvard.edu/abs/2011ApJ...728..137S
%    which said GP is not worth the hassle....

\begin{figure*}
\begin{center}
\includegraphics[scale=0.4]{Figures/emulator_accuracy.eps}
\end{center}
%ZH:  It would be really nice to show ``kappa'' and ``ell'' instead (or in addition) to ``i'' on the x axis.
%     Maybe use the top of the figure to label kappa's and ell's?  Or at least state the kappa and ell ranges in words.
\caption{Accuracy of the emulator based on the \texttt{CFHTemu1}
  simulations. The figure shows the absolute difference between the descriptor
  interpolated at the fiducial parameter setting, and the descriptor
  expected from the \texttt{CFHTcov} simulations (these are the absoulte values of differences which oscillate around zero). The descriptors are
  shown in units of the standard deviation in each bin $i$ (determined
  from the diagonal elements of the \texttt{CFHTcov} covariance
  matrix). We show the accuracy results for the power spectrum (red)
  and the three Minkowski functionals $V_0$ (green), $V_1$ (blue) and
  $V_2$ (black). For reference, we also show, using dashed lines, the
  difference between the expected \texttt{CFHTcov} descriptors and the
  interpolated descriptor at the non--fiducial point $\mathbf{p}=(0.8,-1.0,0.5)$. This non--fiducial point lies beyond the LM $1\sigma$ contour from the simulations shown in Figure \ref{contours3single} right panel, and corresponds to the target accuracy we wish to achieve}
%ZH: This last one is chosen to lie along our 1 (or 2?) sigma contour, right?
%    We should then state this, and make the point that this is the interpolation accuracy we care about,
%    and our accuracy is indeed better than this.
\label{emulatorAccuracy}
\end{figure*}

@@

In order to compute the principal components of our descriptor space,
we use the \texttt{CFHTemu1} simulations, which sample the
cosmological parameters at the $N=91$ points listed in Table
\ref{designtable}, and allow us to compute the $N\times N_b$ model
matrix $M_{pi}=M_i(\mathbf{p})$. Note that this is a rectangular
(non-square) matrix. Following a standard procedure (see, e.g.,
ref.~\citep{astroMLText}), we derive the {\it whitened} model matrix
$\tilde{M}_{pi}$, defined by subtracting the mean (over the $N=91$ models) of each bin,
and normalizing it by its variance (always over thw $N=91$ models). Next we proceed with a singular
value decomposition (SVD) of $\mathbf{\tilde{M}}$,
\begin{equation}
\label{svd}
\mathbf{U}\mathbf{S} \mathbf{V}^T=\frac{\mathbf{\tilde{M}}}{\sqrt{N-1}},
\end{equation}   
%
where $S_{ij}=S_i\delta_{ij}$ is a diagonal matrix and $V^T_{ij}$ is
the $j$--th coordinate ($j=1...N_b$) of the $i$--th principal
component ($i=1...\mathrm{min}[N_b,N]$) of $\mathbf{\tilde{M}}$, with
the index $j$ ranging from $0$ to $N_b-1$. By construction,
$\mathbf{V}$ is $\mathbf{p}$--independent.

@@

This section describes our main results, and is organized as follows.
We begin by showing the cosmological constraints from the CFHTLenS
data for the triplet $(\Omega_m,\sigma_8,w)$, as well as for an
alternative parameterization, $(\Omega_m,\Sigma_8,w)$, with
$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$. In the latter we give a justification on why we fix $\alpha$ to a value of $0.55$. 
We then use our simulations to perform a robustness analysis of the parameter
confidence intervals with respect to the number of PCA components used
in the projection.
%We first use our simulations to perform a robustness analysis
%of the parameter confidence intervals with respect to the number of
%PCA components used in the projection. We then show the cosmological
%constraints from the CFHTLenS data.
%ZH: I reversed the order of the above two.  
%    It is better to first show the constraints,  and only THEN we can discuss their robustness.
%    Also I moved the discussion of \Sigma_8 down below.
We finally study whether the constraints can be tightened by combining
different descriptors. A summary with the complete set of results,
along with the relevant Figures, is shown in Table \ref{summarytable}.
